Security Audit of Safeplug

### 2014-02-12 report/design.tex
rearranged sections

\subsubsection{Initial Plugin Behavior}
Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.  The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.  The other card was the connection to the internet.  We used Wireshark to analyze the network data that we captured \cite{wireshark}.

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.  While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our router back to the internet and captured traffic on both of the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and then send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.

The client computer then navigated to the Pogoplug website to complete the activation process.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the Pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the safeplug\_lighttpd and safeplug\_lighttpd\_config installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade.

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  More information about the configuration is in Section \ref{spconfig}.  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic runs through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

@@

>>>>

@@

\subsubsection{Activation and Setup}
The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{Configuration instructions.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{Proxy Configuration.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

After we finished our configuration, we were taken to our settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{Settings page.}
\label{fig:settings}
\end{center}
\end{figure}

### 2014-02-12 report/old.tex
rearranged sections

\subsection{Traffic Analysis}
\label{sec:traffic}

\subsubsection{Initial Plugin Behavior}
Before allowing the Safeplug box to be connected to the outside world, we attached it to the home connection setup described in Section \ref{sec:proc} and captured traffic for a few minutes on the local network.  From visual inspection (Figure \ref{redlight}), there was certainly something trying to access the internet and displaying an error on its failure.

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth]{redlight.jpg}
                \caption{Safeplug box when only connected to the local network.}
                \label{redlight}
        \end{subfigure}%
        \quad %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.4\textwidth}
          \centering
          \includegraphics[width=.66\textwidth,angle=180]{greenlight.jpg}
                \caption{Safeplug box after connection to the internet, regardless of whether Tor was enabled.}
                \label{greenlight}
        \end{subfigure}
        \caption{Safeplug box during initial setup prior to an internet connection and after activation from the Pogoplug website.}
        \label{fig:lights}
\end{figure}

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.  While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.  In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.

The client computer then navigated to the Pogoplug website to complete the activation processes.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the two lighttpd installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  (More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED is set to green as shown in Figure \ref{greenlight} after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    \subsubsection{Accessing the Device}
    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP. SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
\begin{fileName}
curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{fileName}

Obviously having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

    \subsubsection{Software on the Safeplug}
\label{software}
As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

    \subsubsection{Configuration on the Safeplug}
    \label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.  This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.  The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exitrelay) to use.

\subsection{Attacking the RPC Capability}
As we discovered while enabling SSH, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc! and it contains more options than just SSH enabling.  Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{disabletor}
\caption{Disabling Tor as an insider attack.}
\label{disable}
\end{center}
\end{figure}

\subsubsection{Insider Attack}
Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.  All the attacker would need to know is the IP of the device.  It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of this attack.

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

This seems like a fairly important vulnerability and requires action from Pogoplug to fix.  Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.  If not, perhaps there is some authentication protocol that could be implemented.  The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.

\subsubsection{Website Attack}
An external website can also perform this attack by returning a correctly formatted POST string.  This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.  Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.  We implemented this attack with less than 30 lines of Javascript code (See Appendix A).  The following steps are necessary for the attack to be successful:

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.

The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.  This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.  (Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)

>>>>

\subsubsection{Initial Plugin Behavior}
Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.  The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.  The other card was the connection to the internet.  We used Wireshark to analyze the network data that we captured \cite{wireshark}.

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.  While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our router back to the internet and captured traffic on both of the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and then send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.

The client computer then navigated to the Pogoplug website to complete the activation process.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the Pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the safeplug\_lighttpd and safeplug\_lighttpd\_config installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade.

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  More information about the configuration is in Section \ref{spconfig}.  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic runs through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

### 2014-02-12 report/usability.tex
rearranged sections

\subsection{Terms of Service}
\label{tos}
The first section of the Terms of Service explains how to agree to them:

@@

This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.  The Terms of Service continues by notifying readers that Pogoplug can change them any time they wish:

@@

Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.  It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.  The Terms of Service next includes:

@@

The link included is a dead link and takes the user to a web page with a 404 error.  This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.  In fact, the Tor mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.  The last section of the Terms of Service that stood out described Pogoplug's policy on updates:

@@

\subsection{Internet Use}
\label{inetuse}

\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{Configuration instructions.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{Proxy Configuration.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

After we finished our configuration, we were taken to our settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{Settings page.}
\label{fig:settings}
\end{center}
\end{figure}

\subsubsection{Using the Internet} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

@@

\subsection{Latency}
This is a todo item for Annie.

>>>>

\subsection{Terms of Service}
\label{tos}
The first section of the Terms of Service (TOS) explains how to agree to them:

@@

This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.  The TOS continues by notifying readers that Pogoplug can change them any time they wish:

@@

Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.  It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.  The TOS next includes:

@@

The link included is a dead link and takes the user to a web page with a 404 error.  This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.  In fact, the Tor-talk mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.  The last section of the TOS that stood out described Pogoplug's policy on updates:

@@

\subsection{Internet Use}
\label{inetuse}
Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

@@

\subsection{Latency}
This is a to do item for Annie.
